% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Lianzheng Xie}

\basicInfo{
  \email{lxie0014@student.monash.edu} \textperiodcentered\ 
  \phone{(+61) 0423675635} \textperiodcentered\ 
  \linkedin[lianzheng]{https://www.linkedin.com/in/lianzheng-xie-841b4026a/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Monash University}, Clayton, Australia}{2023– Present}
\textit{Master student} in Information Technology (IT), expected March 2025
\datedsubsection{\textbf{ Monash University}, Clayton, Australia}{2009 -- 2013}
\textit{B.S.} in Information Technology (IT)

\section{\faUsers\ Professional Goal}
\textit As an IT graduate student, I want to solve real-world problems through technology, especially in the field of healthcare. I am passionate about working on innovative projects that combine technology and user needs to develop effective tools for mental health care workers to help reduce workload and improve the quality of patient care.


\section{\faCogs\ Skills}
\textbf{Programming and development skills}
\begin{itemize}[parsep=0.5ex]
  \item Proficient in Python and JavaScript programming languages, good at developing safe and reliable applications.
  \item Experienced in geospatial data handling, cleaning, and visualization using tools like Matplotlib, Pandas, and D3.js.
  \item Experience in front-end development with Vue.js framework to provide users with a friendly interface and smooth interactive experience.
  \item Familiar with API integration, able to design and implement data recording and retrieval systems to ensure safe and seamless data flow.
\end{itemize}

\textbf{Healthcare Technology and user Experience Design}
\begin{itemize}[parsep=0.5ex]
  \item Have a strong interest in the application of technology in the field of mental health care and excel at designing user-centric applications that improve the productivity and accuracy of professionals.
  \item Experience in developing user-friendly interfaces and easy handover workflows to ensure less missing information during shift handover.
\end{itemize}

\textbf{Project management and software engineering}
\begin{itemize}[parsep=0.5ex]
  \item Master the software development life cycle (SDLC), be familiar with agile development methods, and have the ability to collaborate and assign tasks.
  \item Ability to version control and issue tracking via GitHub, maintain high quality code base and manage project progress.
\end{itemize}

\textbf{Data management and visualization}
\begin{itemize}[parsep=0.5ex]
  \item Skilled use of Pandas and Matplotlib and other tools for data cleaning, processing and visualization, to provide data support for decision-making.
  \item Experience developing database-centric systems, such as MySQL and PostgreSQL, that support large-scale data storage and efficient queries.
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/LianzhengXie
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
